---
title: 'Participation Assignment #2'
author: 'Andrew Nalundasan'
Date: 'MM/DD/YYYY'
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r echo=FALSE}
# Course: OMSBA 5210, Seattle University
# Purpose: Participation Assignment #2
# Date: 6/29/2021
# Author: Andrew Nalundasan
```

```{r message=FALSE}
# Load libraries and packages
library(tidyverse)
library(ggplot2)    
library(gridExtra)    # combine graphs into same frame
library(scales)    # to get $ and , on axis in graph
```

# Load and transform data

```{r}
# Load data
oj <- read_csv("OJ_data.csv")

```

# Plot a histogram

```{r}
hist <- ggplot(data = oj, mapping = aes(x=PriceMM))
```

## Basic histogram
```{r}
hist + geom_histogram()
```

## Filled histogram
```{r}
hist + geom_histogram(mapping = aes(fill=Purchase))    # 'Purchase' variable fills in the bars
```

## Histogram - Density
```{r}
hist + geom_density(mapping = aes(fill=Purchase), alpha = 0.5)    # alpha to add transparency
```

# Plot a boxplot

```{r}
bp <- ggplot(data = oj, mapping = aes(x=0))
bp + geom_boxplot(mapping = aes(y=PriceMM))    # Median is ~2.1 First quartile ~ 2.0. Third quartile ~ 2.2
```

## Flipped boxplot
```{r}
bp + geom_boxplot(mapping = aes(y=PriceMM)) + 
  coord_flip() +    # flip coords to make horizontal
  theme_classic()  
```


# Bar graphs

```{r}
# reset original frame to set gender for bar graph
bar <- ggplot(data = oj, mapping = aes(x=STORE))

```

## Classic bar geom
```{r}
# classic bar geom
bar + geom_bar()
```


## Stacked bar graph and counts
```{r}
# stacked bar graph counts
bar <- ggplot(data = oj, mapping = aes(x=STORE, fill=Purchase))
bar + geom_bar()
```

## Proportional stacked bar graph
```{r}

# use position="fill" to get stacked bar graphs
bar + geom_bar(position="fill")
```

## Clustered bar graph of counts
```{r}
# show count level AND balance
# position = "dodge" gets clustered bar graph
bar + geom_bar(position = "dodge")
```


# Additional formatting
```{r}
pa2 <- ggplot(data = oj, mapping = aes(x = STORE, y = SpecialMM, fill = Purchase)) + 
  geom_bar(position="dodge", stat = "summary") + 
  labs(x = "Store",
       y = "Special on MM", 
       title = "Minute Maid sells more than Citrus Hill when on special",
       subtitle = "Minute Maid sales when on special compared to Citrus Hill") + 
  scale_y_continuous(labels = dollar) + 
  theme_classic() + 
  coord_flip() + 
  scale_fill_manual(values = c("dark orange", "chartreuse4"),    # going for an OJ theme here
                    guide = guide_legend(reverse = TRUE))


# show graph
pa2

```

This graph indicates than when Minute Maid (MM) is on special, MM experiences a higher number of purchases over Citrus Hill (CH), MM's main competitor. When MM is running a 40 cent discount, sales at Store 1 skyrocket compared to CH sales. Discounts of ~5 cents do not make much of a difference in sales for either brand as shown by Store 3. 


## Save graph for memo
```{r}
# save previous graph to use in memo
ggsave(filename = "pa2.png", plot = pa2)
```




